Thank You, Next

### 2022-08-03 Manuscript/manuscript_draft.tex
Update manuscript_draft.tex

\documentclass[12pt,a4paper]{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsfonts,amssymb,amsmath,amsthm}
\usepackage{multirow}
\usepackage{multicol}
\setlength{\columnsep}{1.5cm}
\usepackage{setspace}
\usepackage{url}
\usepackage{array}
\usepackage{xfrac}
\usepackage{mwe}
\usepackage{tikz}
\usepackage{lmodern}
\usepackage{flowchart}
\usetikzlibrary{shapes,arrows,positioning,calc,fit}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{color,soul}
%\usepackage[numbers,sort&compress]{natbib}
\usepackage{hyperref}
%\usepackage{cite}
\usepackage{biblatex}
\addbibresource{References.bib}
\newcommand{\tom}[2]{{\color{red}{#1}}\footnote{\textit{\color{red}{#2}}}}

@@

Mutuaisms are among the most widespread species interactions with diverse and dynamic consequences.
Depending on environmental context the outcome of the interaction can range from parasitic to mutualistic. 
Most studies focus on a pair of species interacting in a mutualism, however most observed mutualistic interactions include more than two species. 
These are multi-species mutualisms, where there are multiple partners interacting with the same focal species. 
\hl{The partners can directly impact the focal species through the interactions, \tom{and indirectly impact them through interactions with each other}{***This is true but not something we are well poised to address with our data so might be risky to bring it up.***}. }
The cactus \textit{Cylindriopuntia imbricata} reward partners with extrafloral nectar in exchange for defense by various ant species (primarily \textit{Crematogaster opuntiae} and \textit{Liometopum apiculatum}, though there are many other ant species with smaller populations) from herbivores and seed predators. 
\hl{Using a 20-year collection of demographic data (growth, survival, reproduction, ant partners, herbivory, etc.) from these cacti in New Mexico, we estimate the fitness of the cacti populations with every combination of partners, allowing us to *** understand what accounts for partner diversity in this system *** understand if the current partner diversity of the system is associated with the optimal fitness *** and the impacts of these partners on different vital plant processes across their life history (such as partner impacts on reproduction, survival, or growth). }
We found that different ant partners had different impacts on cacti vital rates suggesting there may be a different 'best' partner during pre-reprodctive life stages than during reproductive life stages, and that the highest cacti fitness is associated with the current partner set (all possible ant partners are available).
Together, these results suggest that complementarity may account for the benefits that these plants experience with partner diversity. 
Our results demonstrate the importance of evaluating a mutualism within a community context and \tom{suggest that even slight differences of rewards between mutualist partners can help promote fitness of the cacti}{Nothing you have reported in the abstract so far really supports this statement.}.

@@

\section*{Context/Introduction}
BASELINE OF MUTUALISMS
Mutualisms are species interactions in which all involved participants benefit. They are among the most widespread species interactions\cite{Chamberlain2014,Stachowicz2005,BoucherDouglasH.1985} with diverse and dynamic consequences.

PAIRWISE VS MULTISPECIES

There are benefits of mutualistic interactions, but there are costs as well, some direct and some indirect. 
Directly, mutualistic partners can sometimes become parasitic, causing harm to the focal mutualist\cite{Bronstein2001a}. 
\tom{More indirectly, these interactions require energy.}{Awkward sentence, and I'm not sure why investment is reward is an indirect cost.} 
\tom{Within a mutualism, each participant offers rewards and in return receives benefits from their partners.}{No new information content in this sentence.} 
These rewards come in many forms (nectar, protection, habitat, etc.), all of which require some investment \cite{Bronstein2001}. 
These investments can be seen as the costs of mutualisms, they are traded for the rewards provided by a partner. 
\tom{Because of these trade-offs}{trade-offs between what and what?}, there are both costs and benefits to a mutualistic interaction\cite{Bronstein2001,Bronstein2001a}, \tom{particularly as the mutualism becomes more complex in the context of its environment}{I don't know what this means.}.\tom{}{Having made it to the end of this paragraph I can't really find any new information here. You are covering very basic aspects of mutualism that were already described in the first paragraph. I would get to the question/problem at the core of this paper more quickly.}

Mutualistic interactions can occur simply between two species, a pairwise mutualism, or between a group of species, a multi-species mutualism\cite{Stanton2013}.\tom{}{Technically all mutualisms are pairwise (++) but they can be combined into many pairs.} 
Pairwise mutualisms may provide \tom{benefits of efficiency in the context of mutualisms}{I don't know what this means}, but \tom{they are not a good investment due to temporal and spatial variation}{Variation in what?}\cite{Waser1996}. 
Despite this, pairwise mutualisms are historically well studied, with most mutualism papers being focused on pairwise interactions. 
These studies are often used to predict outcomes of mutualistic interaction, which may underestimate the combined impacts of multiple partners on the focal mutualist\cite{Stanton2013,Palmer2010}. 
Pairwise interactions do not always indicate what the net interaction will be within a multi-species context\cite{Chamberlain2014,Song2020}. 
When many species are included, variation between partners can occur in functional benefit, lifespan, and competitive rankings, among other factors\cite{Stanton2013}. 
This difference is because in addition to the expected direct benefits of interactions, \tom{they can also indirectly impact the focal mutualist through other partner interactions. }{Again, I would avoid too much discussion of interaction between partners. You don't need interactions between partners to have non-additive effects, and you are priming readers to expect something that the manuscript does not deliver.}
One reason for this lack of predictability is that interactions between partners changes the relationship with the focal mutualist\cite{Afkhami2014}.  
Often the partners interact with each other, either \tom{increasing their performances}{awkward}, with extra rewards, or decreasing them, often by fighting\cite{Boucher1982}. 
This means predicting the rewards of a multi-species mutualism is very difficult.

Multi-species mutualisms are not always \tom{additive}{You have not introduced or defined what you mean by additive / non-additive.}: In theory if multiple partners can all form pairwise mutualisms with a focal species, in a multi-species mutualism \tom{one would expect more benefits for the focal partner than in any one pairwise scenario. }{The logic for this expectation is not sufficiently clear.}
\tom{The reality is much less predictable\cite{Stanton2013,Palmer2010,Song2020}.}{While there is nothing grammatically wrong with sentences like this, they don't really provide any new information. Try to streamline your writing so that every word is working in service of communicating information.} 
The \tom{rewards}{Unclear what you mean by rewards. That word can describe something like nectar or protection, but I think you are referring to fitness benefits} can be as simple as the sum of all pairwise rewards, aka. additivity, they can be increased beyond the sum of all pairwise rewards, synergy, or they can be reduced below the sum of pairwise rewards, sub-additivity\tom{}{Needs editing for grammar}. \tom{Specifically, it can often change the quality of benefits. }{Vague and confusing sentence. What is ``it''?}

Sometimes a partner can confer benefits on the focal mutualist in a pairwise interaction but be a neutral or even antagonistic interactor in a multi-species interaction as partners can vary in quality\cite{Afkhami2014}.\tom{}{This topic sentence feels like it is revisiting points from the previous paragraph. Try to use topic sentence to demarcate narrative movement.} 
Some mutualists are of so low a quality that they are known as freeloaders or cheaters\cite{Song2020,West2007,Frederickson2013} because they return very little benefit, possibly going as far as to be costly to the focal mutualist in exchange for the benefits they receive. 
This change in quality of partners is often due to competition between the partners\cite{Amarasekare2003}.\tom{}{I'm confused here - what change in quality of partners? And how could the existence of freeloaders be driven by competition?} 
Some partners \tom{reduce in quality}{I don't follow. How does a partner reduce in quality? What is the reference point for the reduction?} so drastically that they become antagonistic towards the focal mutualist in these relationships\cite{Afkhami2014,Frederickson2013,Bronstein1994}.\tom{}{This is restating points made earlier that some partners can be costly.} 
\tom{Despite the potential to reduce fitness of the focal mutualist they often remain a partner within the mutualism\cite{Jones2015}.}{Not sure what point you are trying to make with this sentence. Are you trying to suggest something about partner choice? It is not surprising that cheaters associate with their ostensible mutualists, because that is what cheaters are selected to do.}

There are several underlying mechanisms which \tom{promote partner diversity}{These things do not promote partner diversity. They are mechanisms that could account for benefits of partner diversity, if such benefits exist in the first place. That's an important distinction. Therefore if you want to discussed these things then that discussion should be preceded by evidence that partner diversity is or can be beneficial.} that may \tom{shed some light on this}{Shed light on what? What's in the dark?}; specifically, sampling effect,portfolio effect, and complementarity, \tom{three branches of biodiversity ecosystem function theory}{This is good, but I suggest you be more explicit in how this body of theory relates to mutualism, rather than mentioning it in an off-handed way.}\cite{Batstone2018,Hooper2005}.

Sampling effect \tom{states}{The effect does not state anything.} that if partners vary in quality, then a more diverse sample of the partner community may be more likely to include the most beneficial one\cite{Afkhami2014}. 
Particularly, this means that increased diversity of partners means increased probability that some of the partners will be highly beneficial. 
The fitness of a \tom{multi-species mutualistic population}{awkward} experiencing sampling effect will be equal to the fitness of the same population if they interacted only with their strongest partner.

Complementarity states that each partner may account for some part of the benefits, but each has different functional pathways, which together can aid in a broader benefit\cite{Winfree2020}. 
This means that in populations where there is \tom{sufficient interaction}{What do you mean by ``sufficient''?} with the diverse partners there is likely to be increased rewards and \tom{fitness}{Whose fitness?}. 
The fitness of a multi-species mutualistic population \tom{experiencing complementarity}{I don't think sampling effect, complementarity, etc. are ``experienced''.} is likely to be higher than that of any pairwise \tom{mutualistic population}{What is a mutualistic population?}.

Portfolio effect states that each partner is the best under a \tom{different set of conditions}{I could be wrong but I think the standard use of portfolio effect specifically refers to temporal variation.}, meaning across all conditions, meaning there is likely to be an \tom{increase in potential benefits}{Increase relative to what? Benefits to who? What are they potential?}\cite{Winfree2020}. 
Thus, in populations experiencing highly diverse conditions, diverse partners are likely to increase the rewards and fitness of the focal mutualist. 
The fitness of a multi-species mutualistic population experiencing portfolio effect is likely to have a different strongest partner under different conditions, such as year to year, \tom{and will experience similar fitness as they would in a pairwise mutualism with their best partner under any condition}{I don't follow this last part.}.\tom{}{You do a good job describing the mechanisms for positive diversity effects. I think you could rely more heavily on literature for these mechanisms, which is substantial.}

These \tom{biodiversity ecosystem functions}{This is not what they are. They are mechanisms for positive effects of diversity that are most closely associated with the biodiversity-ecosystem function literature, which asks how changes in biodiversity affect ecosystem function} are three which \tom{can be used to explain the diversity of mutualistic relationships in nature}{This is not correct, and it's an important point. These mechanisms cannot explain diversity in mutualisms. They \emph{could} explain positive effects of partner diversity on a focal species, if any such effects occur}\cite{Afkhami2014}. 
If a \tom{system benefits}{I don't think a ``system'' can benefit from anything.} from the existence of multiple partners, one of these functions may be at play. 
\tom{Within the section of mutualistic interaction which have multiple partners, there are many different classifications.}{Awkward and vague - what do you mean by ``classification''?} One type of mutualism that is historically well documented is the interaction between ants and plants\cite{Boege2005,Barton2010}. 
These \tom{interactions can take many forms}{I know what you mean, but use more precise language.}, including \tom{pollination}{ant pollination is rare}, defense, dispersal, \tom{etc}{are these any others besides these three?}\cite{Bronstein2006}. This paper focuses on defensive ant-plant mutualisms. 
These often involve \tom{long-lived}{not necessarily} plants providing extra-floral nectar and/or \tom{habitats}{better to call this ``housing''} to ants which in turn defend them from herbivores\cite{Bronstein1998}.  
\tom{These are very common interactions and have provided many opportunities for empirical studies of mutualisms.}{No information here.} \tom{However, many of these studies have been pairwise rather than investigating the impacts that multiple partners may have on the costs and benefits of a system. }{Hard to follow what gap in the literature you are trying to identify here. There are in fact many studies of ant-plant mutualism that include multiple partners. I think the new thing that you are contributing is asking how diversity in the ant defender guild affects the overall benefits of mutualism for the plant partner.}

This study focuses on the long lived, \tom{faculative}{this is not an adjective that can be applied to a species} \textit{Cylindriopuntia imbricata} (\tom{Cholla cacti}{There are many species of cholla cacti. The common name of this on is tree cholla.}) and its ant mutualists. 
\tom{The}{weird grammar in this sentence} cacti interact with several ant partners, \textit{Crematogaster opuntiae} (\textit{Crem.}) and \textit{Liometopum apiculatum} (\textit{Liom.}) are the most common partners though there are a number of other rarer ant partners, which visit these cacti \tom{in smaller population sizes}{We don't know anything about their population sizes.}.\tom{}{These are the ant partners at the SEV. But the plants have a very wide distribution and likely interact with other ant species elsewhere. So I would not make it sound like this is an exhaustive list of partners for the entire species.} 
The ant partners all provide defense to the cacti from \tom{predators}{insect herbivores and seed predators} in return for \tom{exclusive interaction}{explain} with the plant to take the extra-floral nectar\tom{, meaning they are considered to be within one guild}{awkward}. 
Predators of the cholla include insect herbivores and seed predators, which influence the \tom{reproductive output of the cacti}{also growth, survival, etc.}. 
\tom{Though many multi-species mutualisms result in both costs and benefits, it has been shown that the relationship between these cacti and ants does not result in any major costs for the cacti\cite{Miller2007}.}{I don't know what you mean. EFN production is a pretty clear cost.} 
\tom{However, there are still some small costs which could influence the optimal set of partners.}{This is vague, and tbh I don't know what you mean when you talk about costs.} \tom{This is part of what we will be analyzing in this paper.}{Awkward and unnecessary.}

Though all the ants associated with the \tom{Cholla}{common names are not capitalized} are within one guild, they may not all be equal, \tom{meaning the impacts on the Cholla are complex}{no information here}. In this study, we will answer a number of \tom{questions}{I think this is a good list of questions. Following up on our conversation, we will probably want to re-orient the language to be clear that we are essentially asking about one vs two partners, which is still technically a diversity question but we don't want to oversell the `diversity'.}: 
\begin{enumerate}
	\item Do the Cholla cacti benefit from the multi-species mutualism with multiple ant partners?
	\item What combination of, or individual, ant(s) result in the highest fitness for the Cholla cacti?
	\item Is there evidence of sampling effect, complementarity, or portfolio effect to encourage the current multi-species state of the mutualism?
\end{enumerate}

\tom{In order to answer these questions, I am constructing an Integral Projection Model (IPM)}{This is only one piece of what you are doing. I think the value of the long-term data should be better emphasized.} to calculate the fitness of the Cholla cacti \tom{under different conditions}{What conditions?}. 
\tom{I will be able to quantitatively estimate}{Use plural pronouns and don't use future tense, this is not a proposal.} the fitness of the cholla population if they were to interact with any combination of ant partners, allowing me to determine the best combination of partners. 
Similar approaches have been used to assess the individual qualities of multiple partners\cite{Palmer2010} \tom{but not to determine the optimal combination of partners in a multi-species mutualism}{The Palmer paper and perhaps others have done this. I think the novel contribution of this paper needs to be better explained.}.

We hypothesize that the cacti will experience the highest fitness when interacting with all partners observed in the field, meaning the current mutualism is the \tom{optimal outcome}{I would avoid mention of optimality, which has an evolutionary implication that we are not addressing here}. 
We also hypothesize that complementarity and sampling effect will \tom{play roles in encouraging this}{vague - sharpen this} \tom{diverse mutualism}{A mutualism cannot be `diverse'.}.

\section*{Methods}
\subsection*{Study System}

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsfonts,amssymb,amsmath,amsthm}
\usepackage{multirow}
\usepackage{multicol}
\setlength{\columnsep}{1.5cm}
\usepackage{setspace}
\usepackage{url}
\usepackage{array}
\usepackage{xfrac}
\usepackage{mwe}
\usepackage{tikz}
\usepackage{lmodern}
\usepackage{flowchart}
\usetikzlibrary{shapes,arrows,positioning,calc,fit}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{color,soul}
%\usepackage[numbers,sort&compress]{natbib}
\usepackage{hyperref}
%\usepackage{cite}
\usepackage{biblatex}
\addbibresource{References.bib}
\newcommand{\tom}[2]{{\color{red}{#1}}\footnote{\textit{\color{red}{#2}}}}
\newcommand{\ali}[2]{{\color{pink}{#1}}\footnote{\textit{\color{pink}{#2}}}}

@@

Mutualisms are among the most widespread species interactions with diverse and dynamic consequences.
Depending on environmental context the outcome of the interaction can range from parasitic to mutualistic. 
Most studies focus on a pair of species interacting in a mutualism, however most observed mutualistic interactions include more than two species. 
These are multi-species mutualisms, where there are multiple partners interacting with the same focal species. 
\hl{The partners can directly impact the focal species through the interactions, \tom{and indirectly impact them through interactions with each other}{***This is true but not something we are well poised to address with our data so might be risky to bring it up.***}. }
The cactus \textit{Cylindriopuntia imbricata} reward partners with extrafloral nectar in exchange for defense by various ant species (primarily \textit{Crematogaster opuntiae} and \textit{Liometopum apiculatum}, though there are many other ant species with smaller populations) from herbivores and seed predators. 
\hl{Using a 20-year collection of demographic data (growth, survival, reproduction, ant partners, herbivory, etc.) from these cacti in New Mexico, we estimate the fitness of the cacti populations with every combination of partners, allowing us to *** understand what accounts for partner diversity in this system *** understand if the current partner diversity of the system is associated with the optimal fitness *** and the impacts of these partners on different vital plant processes across their life history (such as partner impacts on reproduction, survival, or growth). }
We found that different ant partners had different impacts on cacti vital rates suggesting there may be a different 'best' partner during pre-reprodctive life stages than during reproductive life stages, and that the highest cacti fitness is associated with the current partner set (all possible ant partners are available).
Together, these results suggest that complementarity may account for the benefits that these plants experience with partner diversity. 
Our results demonstrate the importance of evaluating a mutualism within a community context and \tom{suggest that even slight differences of rewards between mutualist partners can help promote fitness of the cacti}{Nothing you have reported in the abstract so far really supports this statement.}.

@@

\section*{Context/Introduction}
BASELINE OF MUTUALISMS
Mutualisms are species interactions in which all involved participants benefit. They are among the most widespread species interactions\cite{Chamberlain2014,Stachowicz2005,BoucherDouglasH.1985} with diverse and dynamic consequences. 
\ali{The benefits from these interactions are called rewards, but they require investment of resources into the interaction}{I'm honestly not sure if I need to explain this idea? Do I need to include more basic mutualism background? I have tried to shift this so that I cover a small amount and then jump into the idea of partner diversity in mutualisms instead}.

Historically, scientists focused on pairwise mutualisms\cite{Bascompote2019}, however, in recent years multi-species mutualisms have been more heavily studied. 
It has become apparent that partner diversity in mutualisms often leads to non-additive fitness benefits for the focal mutualist\cite{Afkhami2014, Palmer2010}. 
This means the benefits can be greater than, less than, or equal to the sum of the benefits observed in each of the pairwise interactions with the focal mutualist that makes up the multi-species mutualism. 
This is true for many complicated reasons, including interactions between the various partners, niche overlap, temporal resource variation, and differences in partner quality, functional benefit, and competitive ability\cite{stanton2013, Afkhami2014,Boucher1982}.
Often partners have similar resource needs, particularly if they are in the same guild, which can lead to resource competition and fighting, potentially reducing benefits, or to increased quality and frequency of benefits\cite{Bascompote2019,Stanton2003}.
For this reason, pairwise studies cannot be accurately used to predict the outcomes of multi-species mutualisms\cite{Palmer2010, Stanton2013. Chamberlain2014, Song2020} which are more common.
\ali{***** Biodiversity ecosystem function? }{After this I feel like I go straight into the mechanisms which explain the potential positive effects of diversity, but I don't specify that I am talking about those and I also don't talk about any explainations of negative effects? Maybe if I include the connection between BEF theory and mutualisms here it will make a nice bridge to the benefits of diversity?} 
Observational studies on the effects of diverse multi-species mutualism systems are necessary to help us understand the demographic effects of partner diversity in mutualisms.

The diversity of partners in a multi-species mutualism causes varied demographic effects on the population of the focal mutualist which can be explained by a number of mechanisms.
Partners can vary in many ways: in some cases, the quality varies leading to some true mutualist partners, some freeloaders, and even some parasites\{Bronstein1994, Afkhami2014,Song2020,West2007,Frederickson2013}; in other cases, the function of the partner can vary, each offering a different type of reward to the focal mutualist \{Stanton2003}.
Partner quality variations can remain consistent across years and life stages of the focal mutualist or they can shift year to year. 
When partner quality remains consistent across time, meaning one partner is always better or worse than another, the effects of partner diversity on the focal mutualist can be explained by a mechanism called sampling effect.
This is the concept that if partners vary in quality, then a more diverse sample of the partner community may be more likely to include the ``best" one\cite{Batstone2018}.
When a focal mutualist in a multi-species mutualism \ali{experiences}{not sure if this is the right word} sampling effect the fitness of that focal mutualist should be equal to the fitness of the focal mutualist if they interacted only with the ``best" partner. 
In some cases the quality of partners is not constant, rather it varies year to year due to environmental limitations, such as resource shortages and niche shifts.
The effects of partner diversity in these systems can be explained by the portfolio effect, the idea that each partner is the ``best" under a different set of conditions, which vary temporally\cite{Winfree2020,Batstone2018}. 
This mechanism works almost like a financial portfolio, when one partner has a bad year another partner has a good year, meaning the overall fitness benefits of the interactions remain relatively constant across temporal variation\cite{Batstone2018}.
Finally, partners can vary functionally, meaning each partner offers a different type of reward to the focal mutualist. 
The effects of partner functional diversity can be explained by the mechanism complementarity, the idea that each partner may account for some part of the benefits, but each has different functional pathways, which together can aid in broader benefits\cite{Winfree2020,Batstone2018}.
This variation can be both within and outside of a guild, meaning the variation can be very large, such as the difference between pollination and defense among other functions\cite{Bronstein2006}, or relatively small, such as similar rewards across different life stages\{Stanton2003}. 
Complementarity in a system is evidenced by synergistic benefits, meaning the fitness of the focal mutualist is higher than the fitness if the focal mutualist interacted with any one ``best" partner\{Batstone2018}. 
\ali{These three mechanism could explain the positive partner diversity effects on a focal mutualist in a multi-species mutualism, if these benefits exist.}{I am struggling on the transition between this paragraph and the next.}

Multi-species mutualisms are a huge group of interactions which vary considerably. 
While there are many types of mutualistic interactions, including pollination, defense, dispersal, housing, and many more\cite{Bronstein2006} in this paper we will focus on defensive ant-plant mutualisms.
These involve plants which provide extra-floral nectar and/or ``housing'' to ants which in turn defend them from herbivores\cite{Bronstein1998}. 
While these interactions have been well studied\cite{} in the literature, few have considered how diversity within ant defender guilds affect the overall benefits of mutualism for the plant partner.

This study focuses on the long lived \textit{Cylindriopuntia imbricata} (tree cholla) and its ant mutualists. 
Tree cholla have a range which extends across the Southwest United States into Northern Mexico, with our study area set in New Mexico, US at the Sevilleta LTER.
These cacti flower in the spring throughout the summer, their reproductive season, outside of which they are not tended by ants. 
During the reproductive season these plants experience increased visitation by seed predators and herbivores, which influence their reproductive outputs, survival, growth, etc.
There are a number of observed ant partners which interact with the cacti in this part of their range, including \textit{Crematogaster opuntiae} (\textit{Crem.}), \textit{Liometopum apiculatum} (\textit{Liom.}), \textit{Forelius pruinosus}, an unidentified \textit{Camponotus} species, an unidentified \textit{Phenogaster} species, among others. 
The ants which most commonly interact with the cacti are \textit{Liom.} and \textit{Crem.}, while others are seen with low enough frequency that for the purpose of this paper we refer to them as ``other" ants. 
These ant partners are all in the same guild, meaning they all provide denfense to the cacti from insect herbivores and seed predators in return for extrafloral nectar (EFN).
The cacti in this mutualism are each tended by one species at a time, for their entire reproductive season with little turnover until the winter between reproductive seasons. 
Some of the ant partners are more effective defenders than others, with \textit{Liom.} tended reproducing plants experiencing the lowest level of herbivory as shown in Figure \ref{fig:herb}.
This shows that although all the ants associated with the tree cholla are within one guild, they are not all equal and may have different demographic effects on the cacti.

In this paper we will answer a number of questions about the demographic effects of partner diversity in multi-species mutualisms:
\begin{enumerate}
  \item{What are the contrasting demographic effects of multiple partners?}
  \item{What combination of ant partners is associated with the highest fitness for the tree cholla?}
  item{What mechanisms explain the effects of multiple ant partners on the tree cholla?}
\end{enumerate}

To answer these questions we used a long-term dataset of demographic information (size, survival, number of flowers produced or aborted, etc.) and ant partner data (species, number of ants) to track the structure of the population across time as well as individual level impacts of ant partners on the cacti. 
We analyzed the impacts of partner diversity on each individual vital rate (survivial, growth, floral-viability, etc.) with bayesian models, which we used to parameterize an Integral Projection Model (IPM).
With the IPM we moved beyond what has been done in previous studies\cite{Palmer2010} to identify which mechanisms explain the effects of partner diversity on the tree cholla.

We hypothesized that the cacti would experience the highest fitness when interacting with all partners observed in the field, meaning the current mutualism results in the highest fitness for the cacti.
We also hypothesized that complementarity would explain these positive effects of partner diversity in the multi-species mutualism.
\section*{Methods}
\subsection*{Study System}
